---
title: "Lab 1"
author: "Hongyi zhan & Oyundari Batbayar"
date: "2023-09-09"
output: html_document
---

# Introduction

This report provides an analysis of a dataset containing video game scores in relation to various factors such as sales, release year, and critic counts.

### Loading the Data and Packages

```{r load_data, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
video_games <- read.csv("video_games_fall_2023.csv")
library(visreg)
attach(video_games)
```

### Question 1: Visualizing variables (Score, Sales Globally (in millions), Release Year)

```{r}
# Question 1A.
summary(score)

# Question 1B.
boxplot(score, main = "Boxplot for Score", xlab="Score", col = "blue")

# Question 1C.
hist(score, main = "Histogram for Score", ylab = "Frequency", xlab = "Sales Globally (in millions)", breaks = 20, col = "blue")

# Question 1D.
summary(sales_global)

# Question 1E.
boxplot(sales_global, main = "Boxplot for Sales Globally (in millions)", xlab = "Sales Globally (in millions)", col = "green")

# Question 1F.
hist(sales_global, main = "Histogram for Sales Globally (in millions)", xlab = "Sales Globally (in millions)", ylab = "Frequency",breaks = 100, col = "green")

# Question 1G.
summary(release_year)

# Question 1H.
boxplot(release_year, main = "Boxplot for Release Year", xlab = "Release Year", col = "orange")

# Question 1I.
hist(release_year, main = "Histogram for Release Year", xlab = "Release Year", ylab = "Frequency",breaks = 25, col = "orange")

# Question 1J.
summary(count_critic)

# Question 1K.
boxplot(count_critic, main = "Boxplot for Count of Critic", xlab = "Count of Critic", col = "purple")

# Question 1L.
hist(count_critic, main = "Histogram for Count of Critic", xlab = "Count of Critic", ylab = "Frequency",breaks = 10, col = "purple")

# Question 1M. 

par(mfrow=c(1,3))
genre_colors = as.integer(factor(video_games$genre))
plot(sales_global, score, 
     main="Score vs Sales Globally (in millions)", 
     xlab="Sales Globally (in millions)", 
     ylab="Score",
     col = genre_colors, pch=16)

# Scatter plot for score vs release_year
plot(release_year, score, 
     main="Score vs Release Year", 
     xlab="Release Year", 
     ylab="Score",
     col= genre_colors, pch=16)

# Scatter plot for score vs count_critic
plot(count_critic, score, 
     main="Score vs Count of Critic", 
     xlab="Count of Critic", 
     ylab="Score",
     col= genre_colors, pch=16)
```

### Question 2: Simple linear regression

```{r}
# Question 2A.

ols1 = lm(score~sales_global)
summary(ols1)
confint(ols1, 'sales_global', level = 0.95)
visreg(ols1, alpha = 0.05, ylim = c(0,100), main = "Scatterplot of Score vs Sales Globally (in millions)", xlab = "Sales Globally (in millions)", ylab = "Score") 

# Question 2B.

ols2 = lm(score ~ release_year)
summary(ols2)
confint(ols2, 'release_year', level = 0.95)
visreg(ols2, alpha = 0.05, main = "Scatterplot of Score vs Release Year", xlab = "Release Year", ylab = "Score")

# Question 2C.

ols3 = lm(score ~ count_critic)
summary(ols3)
confint(ols3, 'count_critic', level = 0.95)
visreg(ols3, alpha = 0.05, main = "Scatterplot of Score vs Count of Critic", xlab = "Count of Critic", ylab = "Score")

# Question 2D. Can be found in the lab report.
```

### Question 3: Prediction

```{r}
# Question 3A.
coefficients1 <- coef(ols1)

# Extract b0 and b1
ols1_b0 <- coefficients1[1]
ols1_b1 <- coefficients1[2]

# Compute the predicted score for 750,000 sales globally. Note sales globally are measured in millions.
predicted_score1 <- ols1_b0 + ols1_b1 * 0.75
print(predicted_score1)


# Question 3B.
coefficients2 <- coef(ols2)

# Extract b0 and b1 from ols2
ols2_b0 <- coefficients2[1]
ols2_b1 <- coefficients2[2]

# Compute the predicted score for a game released in 2009
predicted_score2 <- ols2_b0 + ols2_b1 * 2009
print(predicted_score2)


# Question 3C. 
coefficients3 <- coef(ols3)

# Extract b0 and b1 from ols3
ols3_b0 <- coefficients3[1]
ols3_b1 <- coefficients3[2]

# Compute the predicted score for a game reviewed by 80 critics
predicted_score3 <- ols3_b0 + ols3_b1 * 80
print(predicted_score3)
```

## Question 4: Multiple regression

```{r}
# Question 4A. Can be found in the lab report. 

# Question 4B. 
ols4 = lm(score ~ sales_global + release_year+count_critic)
summary(ols4)

# Question 4C. Can be found in the lab report. 

# Question 4D. 
coefficients4 <- coef(ols4)
ols4_b0 <- coefficients4[1]
ols4_b1 <- coefficients4["sales_global"]
ols4_b2 <- coefficients4["release_year"] 
ols4_b3 <- coefficients4["count_critic"] 

# Compute the predicted score based on the provided values
predicted_score4 <- ols4_b0 + ols4_b1 * 0.75 + ols4_b2* 2009 + ols4_b3 * 80
print(predicted_score4)

# Question E. Can be found in the lab report.
```


## 5A,B

```{r load_data, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
data = read_csv('video_games_fall_2023.csv')
attach(data)
data <- cbind(data, 'Nintendo'=ifelse(publisher=="Nintendo", 1, 0))
model5 <- lm(score ~ release_year+as.factor(Nintendo), data = data)
summary(model5)
```

With other factors being fixed, the average score for the game that was published by Nintendo would have scored 6.3 points less than the game that was published by any other.

## 5C

```{r}
# Subset the data for Nintendo and non-Nintendo
nintendo_data <- data[data$Nintendo == 1, ]
non_nintendo_data <- data[data$Nintendo == 0, ]

# Create a scatterplot for Nintendo
plot(nintendo_data$release_year, nintendo_data$score, col = "green", pch = 15,
     xlab = "Release year", ylab = "Score", xlim = c(min(data$release_year), max(data$release_year)),ylim = y_range <- range(data$score))

# Add a linear regression line for Nintendo
abline(lm(score ~ release_year, data = nintendo_data), col = "green", lwd = 2, lty = 2)

# Add points and a linear regression line for non-Nintendo
points(non_nintendo_data$release_year, non_nintendo_data$score, col = "blue", pch = 0)
abline(lm(score ~ release_year, data = non_nintendo_data), col = "blue", lwd = 2, lty = 2)

# Add a legend
legend("bottomleft", legend = c("Nintendo", "Non-Nintendo"), col = c("green", "blue"), pch = 15, lty = 2,
       lwd = 2)

# Add a title
title(main = "Relationship between the Score in different release year \n for publish by Nintendo and others")

```

# 6A

```{r}
length(table(genre))
table(genre)
```

# 6B,C,E

```{r}
model6 <- lm(score ~ relevel(as.factor(genre), ref = "Racing"), data = data)
summary(model6)
```

# 6D

```{r}
model7 <- lm(score ~ relevel(as.factor(genre), ref = "Shooter"), data = data)
summary(model7)
```

# 7A,B

```{r}
data2 <- cbind(data, 'Strategy'=ifelse(genre=="Strategy", 1, 0))
model8 <- lm(score ~ as.factor(Nintendo)+as.factor(Strategy)+as.factor(Nintendo)*as.factor(Strategy), data = data2)
summary(model8)
```

# 7C

```{r}
model9 <- lm(score ~ as.factor(Nintendo)+release_year+as.factor(Nintendo)*release_year, data = data)
summary(model9)

plot(nintendo_data$release_year, nintendo_data$score, col = "green", pch = 17,
     xlab = "Release year", ylab = "Score", xlim = c(min(data$release_year), max(data$release_year)),ylim = y_range <- range(data$score))

# Add a linear regression line for Nintendo
abline(109.83809+844.70328,-0.01983-0.41757, col = "green", lwd = 2, lty = 2)

# Add points and a linear regression line for non-Nintendo
points(non_nintendo_data$release_year, non_nintendo_data$score, col = "blue", pch = 2)
abline(109.83809,-0.01983, col = "blue", lwd = 2, lty = 2)

# Add a legend
legend("bottomleft", legend = c("Nintendo", "Non-Nintendo"), col = c("green", "blue"), pch = 2, lty = 2,
       lwd = 2)

# Add a title
title(main = "Relationship between the Score in different release year \n for publish by Nintendo and others")

```
