---
title: "Lab Assignment 1"
author: "Oyundari Batbayar and Hongyi Zhan"
date: "2023-09-09"
output: html_document
---

# Introduction

This report provides an analysis of a dataset containing video game scores in relation to various factors such as sales, release year, and critic counts.

### Loading the Data and Packages

```{r load_data, echo=TRUE, message=FALSE, warning=FALSE}
video_games <- read.csv("C:/Users/oyund/Downloads/video_games_fall_2023.csv")
library(visreg)
attach(video_games)
```
### Question 1: Visualizing variables (Score, Sales Globally (in millions), Release Year)

```{r}
# Question 1A.
summary(score)

# Question 1B.
boxplot(score, main = "Boxplot for Score", xlab="Score", col = "blue")

# Question 1C.
hist(score, main = "Histogram for Score", ylab = "Frequency", xlab = "Sales Globally (in millions)", breaks = 20, col = "blue")

# Question 1D.
summary(sales_global)

# Question 1E.
boxplot(sales_global, main = "Boxplot for Sales Globally (in millions)", xlab = "Sales Globally (in millions)", col = "green")

# Question 1F.
hist(sales_global, main = "Histogram for Sales Globally (in millions)", xlab = "Sales Globally (in millions)", ylab = "Frequency",breaks = 100, col = "green")

# Question 1G.
summary(release_year)

# Question 1H.
boxplot(release_year, main = "Boxplot for Release Year", xlab = "Release Year", col = "orange")

# Question 1I.
hist(release_year, main = "Histogram for Release Year", xlab = "Release Year", ylab = "Frequency",breaks = 25, col = "orange")

# Question 1J.
summary(count_critic)

# Question 1K.
boxplot(count_critic, main = "Boxplot for Count of Critic", xlab = "Count of Critic", col = "purple")

# Question 1L.
hist(count_critic, main = "Histogram for Count of Critic", xlab = "Count of Critic", ylab = "Frequency",breaks = 10, col = "purple")

# Question 1M. 

par(mfrow=c(1,3))
genre_colors = as.integer(factor(video_games$genre))
plot(sales_global, score, 
     main="Score vs Sales Globally (in millions)", 
     xlab="Sales Globally (in millions)", 
     ylab="Score",
     col = genre_colors, pch=16)

# Scatter plot for score vs release_year
plot(release_year, score, 
     main="Score vs Release Year", 
     xlab="Release Year", 
     ylab="Score",
     col= genre_colors, pch=16)

# Scatter plot for score vs count_critic
plot(count_critic, score, 
     main="Score vs Count of Critic", 
     xlab="Count of Critic", 
     ylab="Score",
     col= genre_colors, pch=16)
```

### Question 2: Simple linear regression

```{r}
# Question 2A.

ols1 = lm(score~sales_global)
summary(ols1)
confint(ols1, 'sales_global', level = 0.95)
visreg(ols1, alpha = 0.05, ylim = c(0,100), main = "Scatterplot of Score vs Sales Globally (in millions)", xlab = "Sales Globally (in millions)", ylab = "Score") 

# Question 2B.

ols2 = lm(score ~ release_year)
summary(ols2)
confint(ols2, 'release_year', level = 0.95)
visreg(ols2, alpha = 0.05, main = "Scatterplot of Score vs Release Year", xlab = "Release Year", ylab = "Score")

# Question 2C.

ols3 = lm(score ~ count_critic)
summary(ols3)
confint(ols3, 'count_critic', level = 0.95)
visreg(ols3, alpha = 0.05, main = "Scatterplot of Score vs Count of Critic", xlab = "Count of Critic", ylab = "Score")

# Question 2D. Can be found in the lab report.
```

### Question 3: Prediction

```{r}
# Question 3A.
coefficients1 <- coef(ols1)

# Extract b0 and b1
ols1_b0 <- coefficients1[1]
ols1_b1 <- coefficients1[2]

# Compute the predicted score for 750,000 sales globally. Note sales globally are measured in millions.
predicted_score1 <- ols1_b0 + ols1_b1 * 0.75
print(predicted_score1)


# Question 3B.
coefficients2 <- coef(ols2)

# Extract b0 and b1 from ols2
ols2_b0 <- coefficients2[1]
ols2_b1 <- coefficients2[2]

# Compute the predicted score for a game released in 2009
predicted_score2 <- ols2_b0 + ols2_b1 * 2009
print(predicted_score2)


# Question 3C. 
coefficients3 <- coef(ols3)

# Extract b0 and b1 from ols3
ols3_b0 <- coefficients3[1]
ols3_b1 <- coefficients3[2]

# Compute the predicted score for a game reviewed by 80 critics
predicted_score3 <- ols3_b0 + ols3_b1 * 80
print(predicted_score3)
```

## Question 4: Multiple regression

```{r}
# Question 4A. Can be found in the lab report. 

# Question 4B. 
ols4 = lm(score ~ sales_global + release_year+count_critic)
summary(ols4)

# Question 4C. Can be found in the lab report. 

# Question 4D. 
coefficients4 <- coef(ols4)
ols4_b0 <- coefficients4[1]
ols4_b1 <- coefficients4["sales_global"]
ols4_b2 <- coefficients4["release_year"] 
ols4_b3 <- coefficients4["count_critic"] 

# Compute the predicted score based on the provided values
predicted_score4 <- ols4_b0 + ols4_b1 * 0.75 + ols4_b2* 2009 + ols4_b3 * 80
print(predicted_score4)

# Question E. Can be found in the lab report.
```

